\cvsection{Work Experience}

\begin{cventries}
    \cventry
        {Freelance Software Engineer}
        {Freelance}
        {Remote}
        {February 2023 - Present}
        {
            \begin{cvitems}
                \item {Worked on backend/frontend projects for multinational clients.}
            \end{cvitems}
        }
    \cventry
        {Lead Solana Blockchain Engineer}
        {NFTPort}
        {Tallinn, Estonia - Remote}
        {Mar. 2022 - February 2023}
        {
            \begin{cvitems}
                \item
                    {Lead and implemented a full pledged Solana indexer that's able to handle \emph{6K TPS (transaction per second)} blockchain events which speeds up ingesting and processing overall transactions.}
                \item
                    {Managed the development of production pipeline for all Solana related jobs.}
                \item
                    {Created and simplified event bus handling which does the whole \textbf{ETL (Extract, Transform, Load)} process.}
                \item
                    {Doubled and scaled the API load capacity for Solana related queries and mutations which speeds up user interactions on the API front.}
                \item
                    {Supervised colleagues and assisted on the development of connector API's which helps in connecting the Solana interface to front gateway interface.}
                \item 
                    {\textbf{Tech Stack:} GCP, AWS, Docker, Typescript, Rust, Solana RPC, MongoDB, Redis}
            \end{cvitems}
        }        

    \cventry
        {Lead/Senior Full Stack Engineer}
        {Starshot Software}
        {Lleida, Spain - Remote}
        {Mar. 2019 - March 2022}
        {
            \begin{cvitems}
                \item
                    {Moving Minds - Onebright (formerly CBT Clinics) [onebright.com]}
                \begin{cvsubitems}
                    \item
                        {Drafted the initial proposal changes and timelines for client's platform request.}
                    \item 
                        {Led the feasibility study conducted on the existing client's platform.}
                    \item
                        {Analyzed existing codebase for any feature that will be migrated to increase platform capability.}
                    \item
                        {Established and picked teammates that would work on the project and set expectations the client wants.}
                    \item
                        {Assisted the onboarding process of the lead developer on client’s side this would improve technical communication.}
                    \item 
                        {Fostered new ways for improving developer relations and productivity.}
                    \item 
                        {\textbf{Tech Stack:} C\#, SSO, RabbitMQ, MSSQL}
                \end{cvsubitems}
                \item
                    {Hyst [hyst.co]}
                \begin{cvsubitems}
                    \item 
                        {Developed a blockchain based raffle system on Ethereum following the client's platform request.}
                    \item 
                        {Implemented a microservice connector to connect marketplace to blockchain which could attract crypto ethusiasts to platform.}
                    \item 
                        {\textbf{Tech Stack:} Typescript, Solidity, NodeJS, Express, Azure}
                \end{cvsubitems}
                % \item
                %     {Becton Dickinson [bd.com]}
                % \begin{cvsubitems}
                %     \item
                %         {Assessed the existing web app if feasible to upgrade to latest stack improving the speed and developer workflow.}
                %     \item
                %         {Overhauled the existing web app converting it to latest tech stack.}
                %     \item 
                %         {Supervised the development of the client's platform and communicated frequently for feature updates.}
                %     \item 
                %         {\textbf{Tech Stack:} C\#, MSSQL, Active Directory}
                % \end{cvsubitems}
                \item
                    {American College of Emergency Physicians (ACEP) [acep.org]}
                \begin{cvsubitems}
                    \item 
                        {Headed the creation of a backend that will serve both web and mobile app.}
                    \item 
                        {Assembled a team which comprises of two developers and 1 UI/UX to complete the project on time.}
                    \item 
                        {Diversified the task to co-workers and aligned the timetable to project completion date.}
                    \item 
                        {Implemented new features like SSO and new storage solution that would help the client's platform.}
                    \item 
                        {\textbf{Tech Stack:} C\#, MSSQL, Azure}
                \end{cvsubitems}
                \item
                    {Chessino (Choker) [chokergame.com]}
                \begin{cvsubitems}
                    \item 
                        {Restructured the way updating third party library works speeding up the onboarding process of new developers.}
                    \item 
                        {Outlined changes needed for the platform to accommodate latest ways to connect Unity to backend which improves platform speed.}
                    \item
                        {Reorganized the backend implementation and removed old, deprecated code from outdated version libraries which makes the platform code leaner.}
                    \item 
                        {Lobbied adding multiple documentation which improves the overall readability of the project for new developers.}
                    \item 
                        {Patched security flaws on existing implementation improving platform security.}
                    \item 
                        {Implemented features like match making rank to help users match up with same skilled user.}
                    \item
                        {Coached a colleague developer on how to implement new connection features which would help boost platform speed.}
                    \item 
                        {Created POC for new connection feature and demonstrated on client's team.}
                    \item 
                        {\textbf{Tech Stack:} Elixir, Erlang, PostgreSQL, Unity, C\#}
                \end{cvsubitems}
                \item
                    {Hypercapital [hypercapital.com]}
                \begin{cvsubitems}
                    \item 
                        {Produced a working voting contract on solidity for POC which determines the viability of product.}
                    \item
                        {Led the creation of a POC which calls RPC and logs event that would fit the need of client.}
                    \item 
                        {Presented the POC and arranged the date and timeline of completion to client improving the relationship of Starshot and client.}
                    \item 
                        {Assisted client for their needs and supported the UI flow implementation presented by a colleague.}
                    \item 
                        {\textbf{Tech Stack:} Typescript, Solidity, PostgresSQL, Azure}                   
                \end{cvsubitems}
            \end{cvitems}
        }
        
    \cventry
        {Lead Full Stack Engineer and Blockchain App Developer}
        {Fat Fish Internet Group}
        {Singapore, Singapore - Remote}
        {Mar. 2018 - Mar. 2019}
        {
            \begin{cvitems}
                \item
                    {Nitro Token [nitro.live]}
                \begin{cvsubitems}
                    \item 
                        {Led the new changes for Nitro Token website to improve its SEO visibility.}
                    \item 
                        {Ported an opensource .NET ICO (initial coin offering) platform to run in Unix based architechture that will serve as proof of concept.}
                    \item
                        {Orchestrated the development of the Ethereum based platform and developed its coin system which helps in proving the platform commitment.}
                    \item 
                        {Coordinated directly with client needs to improve platform POC.}
                    \item 
                        {\textbf{Tech Stack:} Golang, Typescript, Solidity, PostgresSQL, MSSQL, C\#}
                \end{cvsubitems}
                \item
                    {SmartFunding [smartfunding.sg and smartfunding.io]}
                \begin{cvsubitems}
                    \item 
                        {Spearheaded the software development of SmartFunding SG improving investor and investee interaction.}
                    \item
                        {Mobilized new cloud infrastructure (AWS instances) to help alleviate heavy traffic which decreases load times.}
                    \item
                        {Advanced the development to production pipeline which simplifies developer life.}
                    \item 
                        {Succeeded in securing policies for cloud infrastructure (AWS) improving trust on platform.}
                    \item 
                        {\textbf{Tech Stack:} PHP, Laravel, MySQL}
                \end{cvsubitems}
                \item
                    {Fatberry [fatberry.com]}
                \begin{cvsubitems}
                    \item
                        {Fostered new feature developments as the lead and added security measures to stop threat actors.}
                    \item 
                        {Familiarized myself with the existing codebase and suggested new development workflows.}
                    \item
                        {Secured all endpoints and policies in the AWS cloud improving overall security.}
                    \item 
                        {\textbf{Tech Stack:} PHP, Laravel, MySQL}
                \end{cvsubitems}
                \item
                    {Beam [beamspace.com]}
                \begin{cvsubitems}
                    \item
                        {Developed the new features for the web and mobile backend that increases its capability to handle latest bookings.}
                    \item
                        {Devised new strategies for quick code, test, and deployment which improve overall developer experience.}
                    \item 
                        {\textbf{Tech Stack:} PHP, CakePHP, MySQL}
                \end{cvsubitems}
                \item
                    {Eureka Pro [medium.com/eurekapro]}
                \begin{cvsubitems}
                    \item 
                        {Created multiple microservices that will be connected to the coin exchange which would add new coins to platform.}
                    \item
                        {Assessed competitors/similar platform offerings and features to know what the platform's missing.}
                    \item
                        {Assisted and headed the buying of coin exchange pre-built code to ease and simplify launching of MVP.}
                    \item 
                        {\textbf{Tech Stack:} Typescript, Solidity, PostgreSQL}
                \end{cvsubitems}
            \end{cvitems}
        }

    \cventry
        {Co-Founder and Lead Software Engineer}
        {Identity Hash}
        {Makati, Philippines}
        {Feb. 2017 - Dec. 2018}
        {
            \begin{cvitems}
                \item
                    {Founded the idea with similar like-minded colleagues on to a vision.}
                \item
                    {Established the product development and product design on the initial MVP.}
                \item
                    {Bolstered team to join pitching competitions for startup visibility.}
                \item
                    {Strengthened and motivated team in times of low morale.}
                \item
                    {Designed the first iteration of platform connecting to Ethereum network which enhanced our confidence on creating the platform.}
                \item 
                    {\textbf{Tech Stack:} Golang, Typescript, Solidity, PostgreSQL}
            \end{cvitems}
        }
        
    \cventry
        {Senior Software Engineer (Ruby - Ruby on Rails)}
        {Talkpush}
        {Makati, Philippines}
        {Feb. 2017 - Oct. 2017}
        {
            \begin{cvitems}
                \item
                    {Furthered develop the NLP (natural language processing) chatbot which led to increase interaction of users to platform.}
                \item
                    {Implemented the candidate search and filter feature for B2B clients; this in turn increases the candidate completion rate.}
                \item
                    {Overhauled the interview creator feature which adds new options for users to input different media types aside from text.}
                \item
                    {Enhanced the backend to support large concurrent access which speeds up the whole platform.}
                \item 
                    {Assisted in production deployment and reviewed peer code changes.}
                \item 
                    {Enhanced the chatbot state machine which would improve bot responsiveness to queries.}
                \item 
                    {\textbf{Tech Stack:} Ruby, RoR, Angular, HTML5, CSS, AWS}
            \end{cvitems}
        }
    
    \cventry
        {Data Scientist (Python) Part-Time}
        {Toucan Pay Lte. Ltd.}
        {Singapore, Singapore - Remote}
        {Jul. 2016 - Nov. 2016}
        {
            \begin{cvitems}
                \item 
                    {Developed ways to use machine learning to analyze human behavior when it comes to paying debts.}
                \item
                    {Formulated scripts to analyze debt scenario for users which helps in determining people that would not pay.}
                \item                        
                    {\textbf{Tech Stack:} Python, Python ML}
            \end{cvitems}
        }
        
    \cventry
        {Lead Software Engineer (Swift / Objective C - iOS)}
        {TNB Ventures (The Co-Foundry)}
        {Ayer Rajah, Singapore - Hybrid}
        {Jan. 2016 - Jan. 2017}
        {
            \begin{cvitems}
                \item
                    {Truuue Stats Pte. Ltd. Singapore}
                \begin{cvsubitems}
                    \item
                        {Engineered the full iOS app from scratch speeding up the manual transaction done beforehand.}
                    \item
                        {Oversaw the whole development pipeline for the mobile programming team.}
                    \item
                        {Inspired fellow co-workers to join weekly team re-creation/building.}
                    \item
                        {Trained a few junior programmers on the flow of the mobile app and backend which speeds up their development journey.}
                    \item                        
                        {\textbf{Tech Stack:} Objective C, Swift, Java, Python}                     
                \end{cvsubitems}
                \item 
                    {Matchimi Philippines}
                \begin{cvsubitems}
                    \item 
                        {Conceived a new searching algorithm for users (candidates) of the service on which it improves the user experience both on app and website.}
                    \item
                        {Improved the Ruby on Rails backend which in turn speeds up the way things work.}
                    \item 
                        {Authored major changes on the front-end to increase user usability.}
                    \item 
                        {\textbf{Tech Stack:} Ruby, RoR, HTML5, CSS, MySQL}
                \end{cvsubitems}
            \end{cvitems}        
        }
        
    \cventry
        {Senior Software Engineer (C++ / C\# - EGM Games and Tools)}
        {Blueprint Gaming Inc.}
        {Makati, Philippines}
        {Mar. 2012 - Nov. 2015}
        {
            \begin{cvitems}
                \item
                    {Crafted multiple titled games that were certified by GLI and released to market.}
                \item
                    {Established a new test-driven development method on newer release games which speed up testing on newer titles.}
                \item 
                    {Implemented security features in all slot machine system loaders which improves overall trust in the running system.}
                \item
                    {Improved drivers for components and peripherals (note receivers, receipt printers) used on slot machines.}
                \item 
                    {Assembled and developed new money control protocol which helps identifying additional foreign money.}
                \item 
                    {Launched hybrid applications (POC) for testing new waters which would help company decide to pursue mobile slot machine apps.}
                \item 
                    {\textbf{Tech Stack:} MS C++, MS MVC, C\#, Python, HTML5, PhoneGAP}
            \end{cvitems}
        }
        
    \cventry
        {Quality Assurance Tester (EGM Games) Part-time}
        {PJ Holdings Inc.}
        {Makati, Philippines}
        {Jun. 2012 - Feb. 2013}
        {
            \begin{cvitems}
                \item
                    {Pioneered the implementation of black box and white box testing techniques in practice to automate testing.}
                \item 
                    {Fostered a new way to easily detect wrong sequences in the game to speed up development.}
                \item
                    {Doubled the speed of checking by automating some of the testing to Selenium with JUnit.}
                \item 
                    {\textbf{Tech Stack:} Selenium, Adobe Air, JUnit, Javascript}
            \end{cvitems}        
        }
        
    \cventry
        {Junior Software Engineer (C++ - EGM Games)}
        {Aruze Gaming America}
        {Makati, Philippines}
        {Apr. 2011 - Mar. 2012}
        {
            \begin{cvitems}
                \item
                    {Maintained the TRTP (theoretical return to player) percentage of casino slot machine games.}
                \item 
                    {Managed the maintenance of testing rigs (CPU) for concurrent simulations.}
                \item
                    {Streamlined the implementation of features and bug fixes using Mantis Bug Tracker from the old ticket tracker overall increasing the productivity of co-workers.}
                \item 
                    {\textbf{Tech Stack:} C++, Bash, Perl, PHP}               
            \end{cvitems}
        }

    \cventry
        {IT Support Desk (Intern)}
        {Teleperformance Philippines}
        {Paranaque, Philippines}
        {Feb. 2010 - Jan. 2011}
        {
            \begin{cvitems}
                \item
                    {Demonstrated ability to manage workstation computers with the assistance of senior IT personnel.}
                \item 
                    {Aided in terminal blocking on the data center.}
                \item 
                    {Assisted in monitoring field area and retrieving malfunction units (headsets, CPU’s, some peripherals).}
                \item
                    {Delegated workstation on company active directory with the assistance of senior IT personnel.}
            \end{cvitems}        
        }

\end{cventries}
